A Bayesian search to find \\high-mass black holes using LIGO data

### 2020-06-24 main.tex
Committed by TeXstudio

\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4-2}

@@

 LIGO is theoretically
sensitive to the merger of binary black holes with total masses up to 500 M\({}_\odot\) which are expected to occur at a
rate of 0-10 yr\(^{-1}\) \citep[\citet{mandel2008rates}]{fregeau2006imbhbRatePrediction}. However, even after \citet{salemi2019search}'s
targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so
far is approximately 80 M\({}_\odot\) \citep{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. High-mass mergers have
very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.

@@

If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400 \text{M}_\odot$) will be detectable by the ground-based gravitational-wave network. According to \citet{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}, gravitational waves from such systems within the detection of the ground-based detectors should occur at a rate of 0-10 yr\(^{-1}\) .  However, even after \citet{salemi2019search}'s
targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so
far is approximately 80 M\({}_\odot\) \citep{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. As demonstrated in ___ High-mass mergers have
very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.

@@

\section{Significance of a high-mass Bayesian Search}\label{significance}}

@@

\caption[p-astro for various O2 foreground triggers]{\label{tab:O2significancesWObcr}p-astro from seveal detection pipelines for a subset of the O2 foreground triggers.}
\centering
\begin{tabular}{llrrrr}
\toprule
Event & Catalog & PyCBC & GstLAL & cWB & IAS\\
\midrule
GW170104 & GWTC-1 & 1.00 & 1.00 & 1.00 & 0.99\\
GW170121 & IAS-1 & NA & NA & NA & 0.99\\
GWC170402 & IAS-2 & NA & 0.09 & NA & 0.68\\
GW170403 & IAS-1 & NA & NA & NA & 0.56\\
IMBHC170423 & IMBH-marginal & NA & 0.00 & 1.00 & NA\\
\addlinespace
GW170425 & IAS-1 & NA & NA & NA & 0.77\\
GW170729 & GWTC-1 & 0.52 & 0.98 & 0.94 & NA\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\documentclass[%
 reprint,
%superscriptaddress,
%groupedaddress,
%unsortedaddress,
%runinaddress,
%frontmatterverbose, 
%preprint,
%preprintnumbers,
%nofootinbib,
%nobibnotes,
%bibnotes,
 amsmath,amssymb,
 aps,
%pra,
%prb,
%rmp,
%prstab,
%prstper,
%floatfix,
]{revtex4}

@@

@@

If intermediate-mass black holes are present, the gravitational waves emitted from the merger of a binary black hole system with at least one intermediate-mass black hole (up to a mass of $400 \text{M}_\odot$) will be detectable by the ground-based gravitational-wave network. According to \citet{fregeau2006imbhbRatePrediction, mandel2008rates,rodriguez2015bbhRatePredictions}, gravitational waves from such systems within the detection of the ground-based detectors should occur at a rate of 0-10 yr\(^{-1}\) .  However, even after \citet{salemi2019search}'s
targeted match-filter based search for gravitational waves from high-mass black holes the largest total mass detected so
far is approximately 80 M\({}_\odot\) \citep{abbott2019gwtc}. A possible explanation for the absence of high mass events may be
due to their misclassification as short-duration instrumental noise transients \citep{blipGlitches}. As demonstrated in ?? High-mass mergers have
very few in-band wave cycles, and hence can easily be mistaken for short-duration instrumental transients.

@@

\section{Significance of a high-mass Bayesian Search}\label{significance}

@@

\caption[p-astro for various O2 foreground triggers]{\label{tab:O2significancesWObcr}p-astro from seveal detection pipelines for a subset of the O2 foreground triggers.}
\centering
\begin{tabular}{llrrrr}
Event & Catalog & PyCBC & GstLAL & cWB & IAS\\
GW170104 & GWTC-1 & 1.00 & 1.00 & 1.00 & 0.99\\
GW170121 & IAS-1 & NA & NA & NA & 0.99\\
GWC170402 & IAS-2 & NA & 0.09 & NA & 0.68\\
GW170403 & IAS-1 & NA & NA & NA & 0.56\\
IMBHC170423 & IMBH-marginal & NA & 0.00 & 1.00 & NA\\
GW170425 & IAS-1 & NA & NA & NA & 0.77\\
GW170729 & GWTC-1 & 0.52 & 0.98 & 0.94 & NA\\
\end{tabular}
\end{table}
